Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-29 FinalPaper/paper.tex
glutton added, stating on gourmand summary now

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors
\end{itemize}

@@

@@

>>>>

\subsection{Planning problem}
\begin{itemize}
	\item Describe the MDP finite horizon planning problem
	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
	\item Describe reward heuristic
	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
	\item The challenge or large branching factors (induced by natural dynamic)
\end{itemize}

@@

%---------------------------------------------------------------------------------------------------------------------------

@@

\subsubsection{GLUTTON}
Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward \emph{R\textsubscript{max}} any action can yield in a state or an upper bound on it. Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive. Glutton uses the following mechanisms to optimize for large branching factors:
\begin{itemize}
	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
	\item Seperating out Natural Dynamics: to reuse variable samples when generator succesors for multiple actions, by seperating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both. 
	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same (s, h) pair. When full, it chooses state-action pars for eviction ans replacement randomly. 
	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely. It compares the optimal action from a h' with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.  
\end{itemize}

%---------------------------------------------------------------------------------------------------------------------------
